|

### 2025-04-25 output/seminar-slideshow.qmd
Correct item indices in negative item parameters
Update "quizz" prompt slide

::: {.r-stack style="color:#90214a;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix} &
    d_1 = 0
  \end{matrix}
$$
:::

::: {.r-stack style="color:#749f4c;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
        -1 \\
        -1
      \end{bmatrix} &
    d_1 = 0
  \end{matrix}
$$
:::

::: {.r-stack style="color:#d76f47;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
        -1 \\
         1
      \end{bmatrix} &
    d_1 = 0
  \end{matrix}
$$
:::
:::::::

@@

::: {.r-stack style="color:#90214a;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix} &
    d_1 = -0.5
  \end{matrix}
$$
:::

::: {.r-stack style="color:#749f4c;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
        -1 \\
        -1
      \end{bmatrix} &
    d_1 = -0.5
  \end{matrix}
$$
:::

::: {.r-stack style="color:#d76f47;"}
$$
  \begin{matrix}
    \mathbf{a}_1 &=
      \begin{bmatrix}
        -1 \\
         1
      \end{bmatrix} &
    d_1 = 0.25
  \end{matrix}
$$
:::
:::::::

@@

:::::: columns
::: {.column .fragment width="33%"}
:::

::: {.column .fragment width="33%"}
:::

>>>>

::: {.r-stack style="color:#90214a;"}
$$
  \begin{matrix}
    \mathbf{a}_2 &=
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix} &
    d_2 = 0
  \end{matrix}
$$
:::

::: {.r-stack style="color:#749f4c;"}
$$
  \begin{matrix}
    \mathbf{a}_3 &=
      \begin{bmatrix}
        -1 \\
        -1
      \end{bmatrix} &
    d_3 = 0
  \end{matrix}
$$
:::

::: {.r-stack style="color:#d76f47;"}
$$
  \begin{matrix}
    \mathbf{a}_4 &=
      \begin{bmatrix}
        -1 \\
         1
      \end{bmatrix} &
    d_4 = 0
  \end{matrix}
$$
:::
:::::::

@@

::: {.r-stack style="color:#90214a;"}
$$
  \begin{matrix}
    \mathbf{a}_2 &=
      \begin{bmatrix}
         1 \\
        -1
      \end{bmatrix} &
    d_2 = -0.5
  \end{matrix}
$$
:::

::: {.r-stack style="color:#749f4c;"}
$$
  \begin{matrix}
    \mathbf{a}_3 &=
      \begin{bmatrix}
        -1 \\
        -1
      \end{bmatrix} &
    d_3 = -0.5
  \end{matrix}
$$
:::

::: {.r-stack style="color:#d76f47;"}
$$
  \begin{matrix}
    \mathbf{a}_4 &=
      \begin{bmatrix}
        -1 \\
         1
      \end{bmatrix} &
    d_4 = 0.25
  \end{matrix}
$$
:::
:::::::

@@

:::::: columns
::: {.column width="33%"}
```{r}
#| fig-width:  5.5
#| fig-height: 5.5
thetas_transf |>
  ggplot(mapping = aes(trait_1, trait_2)) +
  geom_point(alpha = .33, shape = 16, colour = I(PALETTE_BLUE["normal"])) +
  scale_x_continuous(
    minor_breaks = NULL,
    labels = \(breaks) '' |> rep(length(breaks)),
    limits = c(-4, 4),
    expand = expansion(),
    name   = NULL,
    sec.axis = dup_axis(name = "{*&theta;*~1~, *&theta;*~2~}", labels = NULL)
  ) +
  scale_y_continuous(
    minor_breaks = NULL,
    labels = \(breaks) '' |> rep(length(breaks)),
    limits = c(-4, 4),
    expand = expansion(),
    name   = NULL
  ) +
  coord_fixed() +
  theme(
    axis.ticks   = element_blank(),
    axis.line    = element_blank(),
    axis.title   = element_markdown(),
    axis.title.y = element_markdown(),
    panel.grid   = element_blank()
  )
```
:::

::: {.column .fragment width="33%"}
```{r question-mark}
fa(
  "question",
  fill           = "#929acb",
  height         = "200px",
  vertical_align = "-10em",
  margin_left    = "4em"
)
```
:::
